### 2022-01-28 input/conclusion.tex
final draft for conclusion

With the advent of the Edge and IoT era, major distributed services
proposed by our community should be revised to mitigate as much as
possible traffic between \processes.  In this paper, we addressed the
challenge of content indexing, a key service for storage systems, as a
dynamic logical partitioning problem where partitions grow and shrink
to reflect content and replicas locations, as well as infrastructure
changes.

Using an efficient
communication primitive called scoped broadcast, each \process
composing the infrastructure eventually knows the \process hosting the
best replica of a specific content.  The challenge resides in handling
concurrent operations that may impair the propagation of messages, and
in turn, lead to inconsistent partitioning.
%% The major difficulty lies in concurrent operations, each having a
%% different scope, and ensure the correct convergence of the system.  We
%% defined, in particular, multiple properties that highlight this
%% complexity.
%
We highlighted the properties that solve this problem and proposed an
implementation called \NAME.  Our simulations confirmed that
\processes quickly reach consistent partitioning together, and that
the generated traffic remains locked down to partitions.  We also
briefly discussed an improvement to contain the traffic in relevant
autonomous systems.
%% correctness of our protocol as well as the confinement of
%% the traffic only where it is needed.

@@

\noindent As future work, we plan to evaluate \NAME within a concrete
storage system such as \underline{I}nter\underline{P}lanetary
\underline{F}ile \underline{S}ystem
(IPFS)~\cite{henningsen2020mapping}. This would allow us to assess the
relevance of \NAME in a real system subject to high dynamicity, and
compare it against its current DHT-based indexing system that does not
include distance in its operation.
\note{Parler de l'application au CDN (voir tex)}

>>>>

With the advent of the Edge and IoT era, major distributed services
proposed by our community should be revised to mitigate as much as
possible traffic between \processes.  In this paper, we addressed the
challenge of content indexing as a dynamic logical partitioning
problem where partitions grow and shrink to reflect content and
replicas locations, as well as infrastructure changes.  Using an
efficient communication primitive called scoped broadcast, each
\process composing the infrastructure eventually knows the \process
hosting the best replica of a specific content.  The challenge resides
in handling concurrent operations that may impair the propagation of
messages, and in turn, lead to inconsistent partitioning.
%% The major difficulty lies in concurrent operations, each having a
%% different scope, and ensure the correct convergence of the system.  We
%% defined, in particular, multiple properties that highlight this
%% complexity.
%
We highlighted the properties that solve this problem and proposed an
implementation called \NAME.  Our simulations confirmed that
\processes quickly reach consistent partitioning together, and that
the generated traffic remains locked down to partitions.  We also
briefly discussed \NAMEC, an improvement to contain the traffic in relevant
autonomous systems.
%% correctness of our protocol as well as the confinement of
%% the traffic only where it is needed.

@@

At mid-term, we plan to evaluate our proposal within a concrete
storage system such as \underline{I}nter\underline{P}lanetary
\underline{F}ile \underline{S}ystem
(IPFS)~\cite{henningsen2020mapping}. This would allow us to assess the
relevance of the \NAME approach in a real system subject to high
dynamicity, and compare it against its current DHT-based indexing
system that does not include distance in its operation. More generally,
we claim \NAME (or \NAMEC) can constitute a novel building block for
geo-distributed services.  Among the use-cases we have identified,
\NAME can be used to complement content delivery infrastructures by
efficiently sharing between \process attached to the same CDN server
the locatiosn of web objects that have been already downloaded. This
would allow the containment of web traffic even lower in our networks,
and so reduce the overall traffic footprint.
